```{r setup, echo=FALSE}

opts_chunk$set(fig.align='center', fig.width=9, fig.height=7, cache=TRUE, results='hide', warning=FALSE, echo=FALSE, error=FALSE, comment=FALSE,message=FALSE)
```

```{r, results='hide'}

source("psa14_tweets.R")

```


# Test Title

Time-series graph should be here.
```{r, fig.cap="30-minute intervals"}
time.series
```

Counts graph should be here.
```{r}
frequencies
```

Retweets should be here.
```{r}
retweets
```

Ratios should be here.
```{r}
ratios
```

Network graph should be here.
```{r, fig.height=10, fig.width=10}
plot.igraph(rt_graph2, layout=layout.fruchterman.reingold, main="#PSA14 Retweet Network")
```

Links should be here.
```{r}
links
```

Key accounts graph should be here.
```{r, fig.align='center'}
key.accounts
```

Sentiment plot, just a histogram of sentiment scores for all tweets
```{r, fig.align='center'}
sentiment.plot
```

How did the tone change throughout the day, on average?
```{r, fig.align='center'}
sentiment.day.plot
```

How did the tone change throughout the entire conference, on average?
```{r, fig.align='center'}
sentiment.time.weighted
```

Network Graphs
```{r, fig.align='center', fig.height=10, fig.width=10}

par(bg="white", mar=c(1,1,1,1))
plot(g, layout=glay)
title("\nNetwork Graph of Tweets from #PSA14",
    col.main="gray40", cex.main=1.5)

```
